\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-11 evaluation.tex
update in evaluation

\setlength{\tabcolsep}{.72em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{rl rrr rrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results from running the \psharp random and PCT systematic testing schedulers for 100,000 iterations. We report: time in seconds to find a bug (Time to Bug); number of scheduling points when a bug was found (\#SP); and if a bug was found with a particular scheduler (BF?).}
\label{tab:testing}
\end{table*}

>>>>

\setlength{\tabcolsep}{.72em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{rl rrr rrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results from running the \psharp random and PCT systematic testing schedulers for 100,000 iterations. We report: time in seconds to find a bug (Time to Bug); number of scheduling steps when a bug was found (\#SS); and if a bug was found with a particular scheduler (BF?).}
\label{tab:testing}
\end{table*}
